---
title: "Media Coverage in Canada"
---

```{r, include = FALSE}
source('R/packages.R')

tar_load(scan_israeli)
tar_load(scan_palestinian)

# combine datasets 
bound <- rbind(scan_israeli, scan_palestinian)
  
filt <- bound %>% 
  # remove articles that have warning that were published a while ago
  filter(!grepl('This article was published more than', content)) %>% 
  # remove rows that are identical in content
  distinct(content, .keep_all = T) %>% 
  rowwise() %>% 
  mutate(count_isr = sum(str_count(content, "Israel")),
         count_pal = sum(str_count(content, "Palestin")),
         count_ik = sum(str_count(content, "Israelis killed")),
         count_pk = sum(str_count(content, "Palestinians killed")),
         count_host = sum(str_count(content, "hostage")), 
         count_hamas = sum(str_count(content, "Hamas")),
         media_source = sub(".*www.", "", link),
         media_source = sub(c(".ca.*|.com.*"), "", media_source),
         media_source = case_when(media_source == "cbc" ~ "CBC",
                                  media_source == "globalnews" ~ "Global News",
                                  media_source == "nationalpost" ~ "National Post",
                                  media_source == "theglobeandmail" ~ "Globe and Mail",
                                  media_source == "ctvnews" ~ "CTV"))
```

# Who are we discussing? 

We used a grey literature search tool to search Google for articles that contained the words "Israeli" or "Palestinian" on CBC, CTV, and The Globe and Mail websites. 

We then scraped the content of the sites to allow us to do text analysis. After removing duplicates, and articles that were written before Oct 7, we had **483 articles**. We searched for all instances of words that contained any pattern that included "Israel" (e.g., Israel, Israeli, Israelis) and "Palestin" (i.e., "Palestinian", "Palestine", "Palestinians"). We found that Canadian media has significant bias and uses the word Israel* more than double Palestin*.

```{r, echo=F, eval=TRUE}
df <- filt %>% 
  group_by(media_source) %>% 
  filter(media_source != "Global News" & media_source != "National Post") %>%
  summarize(count_isr = sum(count_isr),
            count_pal = sum(count_pal)) %>% 
  drop_na() %>% 
  pivot_longer(cols = c('count_isr', 'count_pal'))

ggplot(df, aes(y = value, x = media_source, fill = name)) + 
  geom_col(position = 'dodge') + 
  theme_classic() + 
  scale_fill_manual(values = c('navyblue', 'darkgreen'), labels = c("Israel*", "Palestin*")) +
  labs(x = "", y = "Count", fill = "Word Pattern")

```

When we get more specific, we see that comparing the phrases "Israelis killed" and "Palestinians killed", we see much lower counts of both phrases being used. CBC has the most dispararity (but note the lowest overall count), with 5x more mentions of Palestinians killed, CTV 2.1 times, and The Globe and Mail 3.5 times. Reuters [reports](https://www.reuters.com/world/middle-east/how-many-palestinians-have-died-gaza-war-how-will-counting-continue-2023-12-06/) at least 16,015 Palestinians have been killed since then, according to Gaza Health Ministry figures, while 1,200 people were killed in Hamas' incursion into Israel, according to Israeli tallies. At this time, approximately 13x more Palestinians have been killed than Israelis.
```{r, echo=F, eval=TRUE}
df <- filt %>% 
  group_by(media_source) %>% 
  filter(media_source != "Global News" & media_source != "National Post") %>%
  summarize(count_ik = sum(count_ik),
            count_pk = sum(count_pk)) %>% 
  drop_na() %>% 
  pivot_longer(cols = c('count_ik', 'count_pk'))

ggplot(df, aes(y = value, x = media_source, fill = name)) + 
  geom_col(position = 'dodge') + 
  theme_classic() + 
  scale_fill_manual(values = c('navyblue', 'darkgreen'), labels = c("Israelis killed", "Palestinians killed")) +
  labs(x = "", y = "Count", fill = "Word Pattern", title = "Israeli Death Count: 1,200 & Palestinian Death Count: 16,015")

```

